Design of Adaptive Constellations and Error Protection Coding for Wireless Network Coding in 5-node Butterfly Networks

### 2017-05-19 all_figures.tex
Added gitignore, figures, template and bibfile

%% LyX 2.1.5 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[letterpaper,english,10pt]{bmc_template/bmcart}
\usepackage{mathptmx}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{array}
\usepackage{float}
\usepackage{units}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[dvips]{graphicx}
\usepackage{setspace}
\usepackage{wasysym}
\usepackage{nomencl}
% the following is useful when we have the old nomencl.sty package
\providecommand{\printnomenclature}{\printglossary}
\providecommand{\makenomenclature}{\makeglossary}
\makenomenclature
\doublespacing

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% LyX specific LaTeX commands.
\special{papersize=\the\paperwidth,\the\paperheight}

%% Because html converters don't know tabularnewline
\providecommand{\tabularnewline}{\\}
%% A simple dot to overcome graphicx limitations
\newcommand{\lyxdot}{.}

\floatstyle{ruled}
\newfloat{algorithm}{tbp}{loa}
\providecommand{\algorithmname}{Algorithm}
\floatname{algorithm}{\protect\algorithmname}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
\usepackage{babel}

\usepackage{cite}
\usepackage{color}
\usepackage{bigdelim,multirow}
\usepackage{tikz}
\usetikzlibrary[arrows,calc,decorations.pathmorphing,backgrounds,positioning,fit,petri,shapes,decorations.markings]
\usepackage{pgfplots}
\usepackage{babel}
\usepackage{multirow}

\usepackage{algpseudocode}
\usepackage{algorithm}

\usepackage{nicefrac}

\usepackage{setspace}

\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

%\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
%\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
%\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

% unnumbered footnote
\makeatletter
\newcommand{\unfootnote}[1]{
  \renewcommand{\@makefnmark}{}
  \footnotetext{#1}
  \renewcommand{\@makefnmark}{\mbox{$^{\@thefnmark}$}}
}
\makeatother

\newcommand{\jj}{\operatorname{j}}      % imaginary unit

\makeatother

\usepackage{babel}
\begin{document}
\begin{frontmatter}

\begin{fmbox}
\dochead{Research Article}

\title{Design of Adaptive Constellations and Error Protection Coding for
Wireless Network Coding in 5-node Butterfly Networks}

\author[
   addressref={aff1},
   email={pavel@prochazka.info}
]{\inits{PP}\fnm{Pavel} \snm{Prochazka}}
\author[
   addressref={aff1},
   email={uricatom@fel.cvut.cz}
]{\inits{TU}\fnm{Tomas} \snm{Uricar}}
\author[
   addressref={aff2},                   % id's of addresses, e.g. {aff1,aff2}
   corref={aff2},                       % id of corresponding address, if any
   %noteref={n1},                        % id's of article notes, if any
   email={david.halls@toshiba-trel.com}   % email address
]{\inits{DH}\fnm{David} \snm{Halls}}
\author[
   addressref={aff1},
   email={jan.sykora@fel.cvut.cz}
]{\inits{JS}\fnm{Jan} \snm{Sykora}}

\address[id=aff1]{%                           % unique id
  \orgname{Czech Technical University in Prague}, % university, etc
  \street{Technicka 2},                     %
  \postcode{16627}                                % post or zip code
  \city{Prague},                              % city
  \cny{CZ}                                    % country
}
\address[id=aff2]{%
  \orgname{Toshiba -- Telecommunication Research Laboratory},
  \street{32 Queen Square},
  \postcode{BS1 4ND}
  \city{Bristol,},
  \cny{UK}
}
\end{fmbox}% comment this for two column layout

\begin{abstractbox}

\begin{abstract} % abstract
In this paper we focus on the design of a reliable communication scheme
for generic 5-node Wireless Butterfly Networks (WBN). Since the WBN
represents a natural extension of the basic 2-way relay communication
channel, we follow the paradigm of \emph{Wireless Physical Layer Network
Coding} and we show that the design of novel adaptive constellations\emph{
} is desirable to exploit the promising performance of wireless network coding in WBN.
We introduce a \emph{systematic constellation design} algorithm and
we show that the proposed constellations are capable of outperforming
conventional point-to-point modulations in WBN over the whole range
of channel signal to noise ratios. To further support the applicability of the proposed
constellations in a practical system, we integrate a simple binary
channel coding scheme, providing a robust \emph{adaptive modulation
and coding scheme} for relaying in symmetric WBNs with arbitrary channel
conditions.
\end{abstract}

\begin{keyword}
\kwd{wireless network coding}
\kwd{butterfly network}
\kwd{relaying}
\kwd{superposition coding}
\kwd{superposition modulation}
\end{keyword}

% MSC classifications codes, if any
%\begin{keyword}[class=AMS]
%\kwd[Primary ]{}
%\kwd{}
%\kwd[; secondary ]{}
%\end{keyword}

\end{abstractbox}

\end{frontmatter}

\section{Introduction}

The invention of Wireless Network Coding\emph{ }(WNC) has indeed provided
a means for a significant enhancement in wireless system performance
\cite{Popovski-Yomo_2007a,Nazer-Gastpar_2011-IEEE-P,Zhang-Liew-Lu_2012}.
However, WNC processing has also revealed several non-trivial research
problems which do not have counterparts in conventional point-to-point
or multi-user systems, like the sensitivity to channel parameterization
\cite{Koike-Popovski-Tarokh_2008,Liu-Tao-Xu_2011-ICC,Yasami-Razi-Abedi_2011,Uricar-Sykora_2011}
or challenging multi-source transmission synchronization \cite{Zhang-Liew-Lam_2006b-ITW,Rosetto-Zorzi_2009-SPAWC,Huang-Wang-Song-Guo-Jamalipour_2012-IEEE-T-WC}.
Furthermore, the specific characteristics of multi-node WNC systems
can call also for novel constellation design approaches (see e.g.
\cite{Uricar-Sykora_2011,Prochazka-Uricar-Halls-Sykora_2015-ICC}).

In WNC the transmitted information symbols are allowed to interact
directly in the constellation space, inducing a specific set of requirements
on the constellations' properties and characteristics (see e.g. \cite{Uricar-Sykora_2011,Prochazka-Uricar-Halls-Sykora_2015-ICC}).
Generally we can declare \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
that any constellation suitable for the specific nature of WNC processing
should be able to form\emph{ a superimposed constellation} with an
appropriate structure at all receiving nodes (allowing direct decoding
of specific WNC functions of user data from the received non-orthogonal
signals \cite{Nazer-Gastpar_2008-ISIT,Sykora-Burr_2011-TVT}) and
simultaneously it should be able to exploit the \emph{broadcast nature
}of wireless channels (allowing a reduction in the consumption of
channel resources in the system \cite{Popovski-Yomo_2007a}). Since
both of these properties hinge on the actual SNR conditions in the
system, the constellation design itself can become a relatively challenging
task.

One of the first attempts to design a suitable multi-source constellation
for communication in a multi-node WNC system was introduced in our
previous work \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}, where
the \emph{adaptive 2-source constellations} for WNC-based communication
in a 5-node \emph{Wireless Butterfly Network} (WBN) were developed.
However, the results presented in \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
are limited to an uncoded system, which significantly limits its practical
applicability.

In this paper we extend the communication scheme from \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}
by appending appropriate \emph{error protection coding} to the system,
resulting in a practical channel-coded adaptive communication scheme
for WBN. We provide the following results and contributions:
\begin{enumerate}
\item We summarize the \emph{systematic constellation design algorithm}
from \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC} and we provide
additional numerical results analysing its promising performance.
\item We revise and extend the results discussing the \emph{adaptive capabilities
of the constellations, }including \emph{the constellation mapping
regions} for adaptive WBN relaying\emph{.}
\item We validate the proposed design in a \emph{real-world HW setup}, including
the HW evaluation of adaptive system performance.
\item We show how the \emph{channel coding} can be integrated into the proposed
constellation design, including the analysis of proper source transmission
rates.
\item We evaluate numerically the performance of the resulting \emph{adaptive
modulation and coding} scheme for a wide range of channel conditions
in the WBN.
\item We show that the proposed design is viable even if the real-world
conditions induce some deviation from the assumed system model.
\end{enumerate}
The rest of the paper is organized as follows. The system model, including
all necessary definitions and details about WNC processing in WBNs
is summarized in Section~\ref{sec:CTUpp_SystemModel}. A systematic
\emph{constellation design algorithm} for WBNs is revised in Section~\ref{sec:CTUpp_Euclidean-Distance-based-Constel}.
The performance analysis of the proposed constellations (including
the HW evaluation) in an uncoded system is available in Section~\ref{sec:CTUpp_Performance-Analysis-Uncoded}.
Section~\ref{sec:CTUpp_Adaptive-Constellation-Design} discusses
an adaptive constellation design and Section~\ref{sec:CTUpp_Channel-Coding}
introduces the channel coding extension to the system. The performance
of the novel adaptive modulation and coding scheme is analyzed in
Section~\ref{sec:CTUpp_Performance-Analysis-Coded}, including a
simple robustness analyzis. Concluding remarks are summarized in Section~\ref{sec:CTUpp_DiscussionConclusions-etc}.

\section{WNC Relaying in Wireless Butterfly Network\label{sec:CTUpp_SystemModel}}

We assume a \emph{symmetric} WBN model \cite{Uricar-Qian-Sykora-Mow_2013-WCNC,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}
with a half-duplex constraint (Fig. \ref{fig:CTUpp_Information_flows}).
An example practical scenario complying with the WBN model is a communication
among vehicles and road-side infrastructure nodes for traffic information
exchange on a bidirectional highway within two time slots \cite{Ho-Liew-Lu}.
The direct channels between the intended source$\rightarrow$destination
pairs are not available in WBN and thus the help of the intermediate
relay node is necessary to enable end-to-end communication. Please
note that in this paper we do not limit our attention to the above
mentioned special example of a high-speed, vehicle-based WBN.

\subsection{Relaying Strategy}

An information-theoretic relaying strategy (based on Superposition
Coding (SC) \cite{Cover-Thomas_ElemInfTheory,Han-Kobayashi_1981,Shende-Rajan-2012-NCC,Popovski-Carvalho_2008})
for WBNs was proposed in \cite{Uricar-Qian-Sykora-Mow_2013-WCNC,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}.
The fundamental idea of the SC-approach is to split each data symbol
$\mathbf{d}_{i}$ at source $i\in\left\{ A,B\right\} $ into the \emph{basic
part} $\mathbf{d}_{i}^{b}=[d_{i,0}^{b},\dots,d_{i,N_{b}-1}^{b}]$
and the \emph{superposed part} $\mathbf{d}_{i}^{s}=[d_{i,0}^{s},\dots,d_{i,N_{s}-1}^{s}]$,
$d_{i,n}^{b},\,d_{i,n}^{s}\in\left\{ 0,1\right\} $, and then process
each of the resulting data streams separately throughout the system
(see Fig. \ref{fig:CTUpp_Information_flows}). While the basic part
represents a \textquotedbl{}true WNC\textquotedbl{} information stream
(limited by the amount of available HSI) in the system, the superposed
part defines the \textquotedbl{}routed\textquotedbl{} information
which is appended on top of the WNC stream to exploit any potential
spare capacity of related channels in the system (see \cite{Uricar-Qian-Sykora-Mow_2013-WCNC,Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}
for more details). A simplified description of SC-based relaying in
an uncoded WBN system is summarized in Table~\ref{tab:CTUpp_SC-relaying-scheme}
and depicted in Fig.~\ref{fig:CTUpp_Information-flow-uncoded-block-scheme}.
\begin{table}
\centering{}%
\begin{tabular}{|>{\raggedright}p{0.95\columnwidth}|}
\hline 
\textbf{Step 1: Source transmission}
\begin{itemize}
\item Source $S_{i},\,i\in\left\{ A,B\right\} $ maps its data symbol $\mathbf{d}_{i}=\left[\mathbf{d}_{i}^{b};\mathbf{d}_{i}^{s}\right]$
into a $\left(N_{b}+N_{s}\right)$-bit superposition modulation symbol
\begin{equation}
s_{i}=\mathcal{A}^{i}\left(\left[\mathbf{d}_{i}^{b};\mathbf{d}_{i}^{s}\right]\right),\label{eq:CTUpp_OverallSourceStreams}
\end{equation}

\item $S_{A},\,S_{B}$ simultaneously transmit their signals to the relay
and unintended destinations (Fig.~\ref{fig:CTUpp_Information_flows}).
\item Relay receives
\begin{equation}
x=h_{AR}\mathcal{A}^{A}\left(\left[\mathbf{d}_{A}^{b};\mathbf{d}_{A}^{s}\right]\right)+h_{BR}\mathcal{A}^{B}\left(\left[\mathbf{d}_{B}^{b};\mathbf{d}_{B}^{s}\right]\right)+w_{R}
\end{equation}

and decodes $\left[\mathbf{d}_{A}^{s};\mathbf{d}_{B}^{s};f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})\right]$,
where $f$ is a hierarchical WNC function \cite{Sykora-Burr_2011-TVT}.

\item $D_{j}$ receives
\begin{equation}
z_{j}=h_{ij}\mathcal{A}^{i}\left(\left[\mathbf{d}_{i}^{b};\mathbf{d}_{i}^{s}\right]\right)+w_{j},\label{eq:CTUpp_Dj_received}
\end{equation}
where $i,\,j\in\left\{ A,B\right\} ,\,i\neq j$ and stores the signal
for further processing.\end{itemize}
\tabularnewline
\hline 
\textbf{Step 2: Relay broadcast}
\begin{itemize}
\item Relay sends $N_{R}=2N_{s}+N_{b}$-bit modulation symbol to both destinations:
\begin{equation}
s_{R}=\mathcal{A}^{R}\left(\left[\mathbf{d}_{A}^{s};\mathbf{d}_{B}^{s};f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})\right]\right).\label{eq:CTUpp_relay_output}
\end{equation}

\item $D_{j}$ ($i,\,j\in\left\{ A,B\right\} ,\,i\neq j$) decodes:

\begin{itemize}
\item $\left[\mathbf{d}_{A}^{s};\mathbf{d}_{B}^{s};f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})\right]$
(from the relay signal (\ref{eq:CTUpp_relay_output}))
\item $\mathbf{d}_{i}^{b}$ (from the stored signal $z_{j}$ (\ref{eq:CTUpp_Dj_received}),
after interference cancellation (IC) of known $\mathbf{d}_{i}^{s}$)
\item $\mathbf{d}_{j}^{b}$ (from $\mathbf{d}_{i}^{b}$ and $f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})$,
using a standard WNC decoding \cite{Sykora-Burr_2011-TVT})
\end{itemize}
\item $D_{j}$ merges $\mathbf{d}_{j}^{b}$ with $\mathbf{d}_{j}^{s}$ to
obtain the desired $\left[\mathbf{d}_{j}^{b};\mathbf{d}_{j}^{s}\right]$.\end{itemize}
\tabularnewline
\hline 
\end{tabular}vskip1ex\caption{SC-based relaying scheme in uncoded WBN}.\label{tab:CTUpp_SC-relaying-scheme}
\end{table}

\subsection{System Model}

For the sake of simplicity of the constellation design analysis, we
provisionally assume that the system is uncoded\footnote{ Modification of the system model for the coded case will be provided
in Section~\ref{sec:CTUpp_Channel-Coding}, together with a discussion
on the design of individual channel encoders for particular information
streams in the system.}. The signal space representations of the transmitted channel symbols
are $s_{A}=\mathcal{A}^{A}\left(\mathbf{d}_{A}\right)$, $s_{B}=\mathcal{A}^{B}\left(\mathbf{d}_{B}\right)$,
where $\mathcal{A}^{i}\left(\centerdot\right)$ is the memoryless
constellation mapper and $\mathbf{d}_{i}$ is the source $i\in\left\{ A,B\right\} $
data symbol. Each communication round can be divided into two phases
(Fig. \ref{fig:CTUpp_Information_flows}). In the first phase (Multiple
Access \textendash{} MA phase) both sources $S_{A},\,S_{B}$ simultaneously
transmit their signal to the relay, which receives a noisy superimposed
constellation:
\begin{equation}
x=h_{AR}s_{A}+h_{BR}s_{B}+w_{R}.\label{eq:CTUpp_relay-received}
\end{equation}
Additionally, the source $S_{i}$ ($i\in\{A,B\}$) transmission is
overheard (at no cost) by its \textquotedbl{}unintended\textquotedbl{}
destination $D_{j}$ ($j\in\{A,B\},\,j\neq i$) as:
\begin{align}
z_{j} & =h_{ij}s_{i}+w_{j}\label{eq:CTUpp_HSI_observation}
\end{align}
Even though the overheard information (\ref{eq:CTUpp_HSI_observation})
does not carry the desired data for the respective destination, it
can be efficiently exploited to enable WNC-based processing in WBNs
\cite{Uricar-Qian-Sykora-Mow_2013-WCNC}. We denote the specific overheard
information as the \emph{Hierarchical Side Information} (HSI) \cite{Uricar-Qian-Sykora-Mow_2014-IEEE-T-WC}.

The relay performs WNC-based decoding \cite{Sykora-Burr_2011-TVT}
of the received signal and broadcasts the decoded WNC (hierarchical)
information as $s_{R}$ to $D_{A},\,D_{B}$ in the second phase (Broadcast
\textendash{} BC phase). Both destinations are able to decode the
desired data using the relay's (hierarchical) signal (\ref{eq:CTUpp_relay-received})
and the overheard HSI (\ref{eq:CTUpp_HSI_observation}) if a proper
WNC processing is employed in the system.

Scalar complex channel coefficients $h_{ij}$, $i,j\in\{A,B,R\}$,
$i\neq j$ are assumed to be constant during the communication round
and known at the respective receiving node. Zero mean i.i.d. complex
Gaussian noise sample $w_{i}$, $i\in\{A,B,R\}$ has variance $\sigma_{i}^{2}$.
Signal to Noise Ratios (SNRs) in the system are given by ($\gamma_{{\rm {MAC}}}$,
$\gamma_{{\rm {HSI}}}$, $\gamma_{{\rm {BC}}}$), where $\gamma_{{\rm {MAC}}}$
is the SNR on the source$\rightarrow$relay multiple-access channel
\textendash{} MAC ($\left(S_{A},\,S_{B}\right)\rightarrow R$), $\gamma_{{\rm {HSI}}}$
is the SNR on the unintended source$\rightarrow$destination (HSI)
channels ($S_{A}\rightarrow D_{B}$, $S_{B}\rightarrow D_{A}$) and
$\gamma_{{\rm {BC}}}$ is the SNR on the relay$\rightarrow$sources
broadcast channel ($R\rightarrow\left(D_{A},\,D_{B}\right)$).

\section{Superposition Modulation Design\label{sec:CTUpp_Euclidean-Distance-based-Constel}}

In this section we summarize the design of constellation mappers $\mathcal{A}^{A},\,\mathcal{A}^{B}$
as presented in \cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}. The
output constellation is created as
\begin{equation}
s=\mathcal{A}\left(\left[\mathbf{d}^{b};\mathbf{d}^{s}\right]\right)=\sum_{n_{s}=0}^{N_{s}-1}L_{n_{s}}^{s}(2d_{n_{s}}^{s}-1)+\sum_{n_{b}=0}^{N_{b}-1}L_{n_{b}}^{b}(2d_{n_{b}}^{b}-1),\label{eq:CTUpp_superpositionModulation}
\end{equation}
where $L_{n}^{b},\,L_{n}^{s}$ are \emph{Superposition Modulation}
\cite{Hoeher-Wo_2011-IEEE-M-COM} \emph{scaling coefficients.}

The coefficients $L_{n}^{b},\,L_{n}^{s}$ (\ref{eq:CTUpp_superpositionModulation})
are generally taken from the set of complex numbers. However, for
the sake of simplicity we limit the scaling coefficients $L_{n}^{b},\,L_{n}^{s}$
to a purely imaginary or real numbers. Even though that this simplified
approach can potentially result in a sub-optimal performance in fading
channels (complex channel coefficients $h_{iR}$, $i\in\{A,B\}$ can
rotate the component superposition constellations), we follow this
simplification to show the basic ideas of the proposed superposition
modulation design. The extension to general complex $L_{n}^{b},\,L_{n}^{s}$
can naturally embrace the source phase pre-rotation \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008},
which virtually reverts the fading channel to the conventional Additive
White Gaussian Noise (AWGN) channel with $\varangle h_{ij}=0$.

As shown in Table~\ref{tab:CTUpp_SC-relaying-scheme}, the basic
and superposed parts of the source information are processed in a
different way through the system and so we will discuss the constellation
design for these two specific information streams separately. We briefly
introduce the incentives and main ideas of the design for the superposed
and basic parts, and then we summarize the complete multi-source constellation
design in a systematic algorithm.

\subsection{Constellation Design: Basic part\label{sub:CTUpp_basic-part}}

A specific WNC function $f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})$
has to be decoded by the relay (Table~\ref{tab:CTUpp_SC-relaying-scheme})
and hence some overlapping of symbols in the superimposed constellation
(observed by the relay node) can be allowed, resulting in improved
Euclidean distance properties. More precisely, two (or more) pairs
of basic information symbols $\left(\mathbf{d}_{A}^{b},\,\mathbf{d}_{B}^{b}\right)$,
$\left(\mathbf{d'}_{A}^{b},\,\mathbf{d'}_{B}^{b}\right)$ can be allowed
to fall into the same point in the superimposed constellation:
\begin{equation}
s_{A}\left(\mathbf{d}_{A}^{b}\right)+s_{B}\left(\mathbf{d}_{B}^{b}\right)=s'_{A}\left(\mathbf{d'}_{A}^{b}\right)+s'_{B}\left(\mathbf{d'}_{B}^{b}\right),\label{eq:CTUpp_exclusive-law}
\end{equation}
if and only if they belong to the same WNC function output, i.e. iff
$f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})=f(\mathbf{d'}_{A}^{b},\mathbf{d'}_{B}^{b})$,
where $f(\centerdot,\centerdot)$ is the hierarchical WNC function\cite{Sykora-Burr_2011-TVT}.
In this case the overlapping symbols produce the \emph{same hierarchical
output}, which can be successfully resolved by the destination, if
matching HSI information is available (Table~\ref{tab:CTUpp_SC-relaying-scheme}).
The particular choice of the scaling coefficients $L_{A,n}^{b},\,L_{B,n}^{b}$
generally depends on the particular choice of the hierarchical WNC
function\footnote{Modulo-sum \cite{Hekrdla-Sykora_2013,Prochazka-Uricar-Halls-Sykora_2015-ICC,Prochazka-2016}
and bit-wise exclusive-or (XOR) \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew-Lu_2012}
hierarchical functions are commonly discussed in the WNC literature,
however, unlike the bit-wise XOR, implementation of channel coding
for the Modulo-sum mapping is a standalone research problem and hence
it is out of the scope of this paper.}. In the rest of this paper we discuss the constellation design for
the \emph{bit-wise exclusive-or} WNC function ($f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})=\mathbf{d}_{A}^{b}\oplus\mathbf{d}_{B}^{b}$,
where $\oplus$ is the bit-wise XOR operation) \cite{Zhang-Liew-Lu_2012}.

Suitable overlapping of constellation symbols at the relay is provided
by letting both sources transmit at the same power level, i.e. $L_{A,n}^{b}=L_{B,n}^{b}$
\cite{Prochazka-Uricar-Halls-Sykora_2015-ICC}. It can be easily shown
that if these superposition modulation (\ref{eq:CTUpp_superpositionModulation})
coefficients are chosen as $L_{A,n}^{b}=L_{B,n}^{b}=3^{\left\lfloor n/2\right\rfloor }$
(for even $n$) and $L_{A,n}^{b}=L_{B,n}^{b}=\jj3^{\left\lfloor n/2\right\rfloor }$
(for odd $n$), the received superimposed constellation at the relay
will have overlaps only among those constellation symbols (\ref{eq:CTUpp_exclusive-law})
which have the same hierarchical WNC output i.e. $f(\mathbf{d}_{A}^{b},\mathbf{d}_{B}^{b})=f(\mathbf{d'}_{A}^{b},\mathbf{d'}_{B}^{b})=\mathbf{d}_{A}^{b}\oplus\mathbf{d}_{B}^{b}=\mathbf{d'}_{A}^{b}\oplus\mathbf{d'}_{B}^{b}$.

\subsection{Constellation Design: Superposed part\label{sub:CTUpp_superposed-part}}

The superposed information given by $\mathbf{d}_{A}^{s},\,\mathbf{d}_{B}^{s}$
has to be decoded separately by the relay (Table~\ref{tab:CTUpp_SC-relaying-scheme}),
and hence a source constellation avoiding all potential overlaps in
the superimposed constellation (observed by the relay node) is desirable.
In an AWGN channel ($h_{AR}=h_{BR}=1$ in Fig.~\ref{fig:CTUpp_Information_flows})
this can be simply achieved by mapping the information bits to the
real-valued Amplitude Shift Keying (ASK) constellation at $S_{A}$
and purely imaginary-valued ASK constellation at $S_{B}$ (or vice
versa). Hence, in AWGN, the resulting superimposed constellation at
the relay will form a regular QAM constellation without any overlapping
of constellation symbols. For the assumed superposition modulation
(\ref{eq:CTUpp_superpositionModulation}), this can be easily achieved
by setting the coefficients as $L_{A,n}^{s}=2^{n}$ and $L_{B,n}^{s}=\jj\cdot2^{n}$.
\begin{algorithm}[H]
\input{alg4_final_TWC.tex}\caption{Constellation design for fixed $N_{b},\,N_{s}$.\label{alg:CTUpp_ButterflyConstellationDesign} }
\end{algorithm}

\subsection{Systematic Constellation Design Algorithm\label{sub:CTUpp_const_design}}

To accommodate both the basic and superposed information streams into
a joint source constellation, the scaling coefficients of basic information
streams ($L_{n}^{b}$) must be pre-scaled by a factor $2^{N_{s}}$
to ensure that they lie above the largest scaling coefficient of the
superposed part. The basic stream (WNC) is thus preferred over the
superposed one (routing) in order to maximize the overall throughput
of the system. The systematic constellation design for arbitrary $N_{b},\,N_{s}$
is summarized in Algorithm~\ref{alg:CTUpp_ButterflyConstellationDesign}.

The basic principle of source constellation design is illustrated
in Fig.~\ref{fig:CTUpp_ConstellationDesignExample} ($N_{b}=2,\,N_{s}=1$)
and some example sets of source constellations with constant $N_{b}+N_{s}=2$
are depicted in Fig.~\ref{fig:CTUpp_ConstellationDesign_NbNs2}.

\section{Performance Analysis I: Uncoded System\label{sec:CTUpp_Performance-Analysis-Uncoded}}

For the sake of simplicity of the theoretical performance analysis,
we assume that source$\rightarrow$relay channels in WBN are AWGN\footnote{Note that this also includes the system with perfect source phase
prerotation \cite{Koike-Popovski-Tarokh_2009a,Zhang-Liew_2010,Anxin-Yuan-Kayama_2008},
which can be obtained by a generalization of the scaling coefficients
as $L'_{n}=L_{n}e^{-\jj\measuredangle h_{SR}}$, where $h_{SR}$ is
the corresponding source$\rightarrow$relay channel.} (i.e. $h_{iR}=1$ for $i\in\{A,B\}$). We evaluate the throughput
analytically as $(N_{b}+N_{s})\cdot(1-P_{e}^{\mathrm{FER}})$, where
$P_{e}^{\mathrm{FER}}$ denotes the frame error rate. Due to the system
symmetry we evaluate the throughput of $S_{A}\to D_{A}$ only. We
set the frame length to $M=768$ symbols (to match the HW evaluation)
and the relay output mapper $\mathcal{A}^{R}$ will be defined as
a conventional ($2^{N_{b}+2N_{s}}$$)$-QAM constellation. All performance
metrics in the symmetric WBN are evaluated as a function of the actual
SNRs ($\gamma_{{\rm {MAC}}},\,\gamma_{{\rm {HSI}}},\,\gamma_{{\rm {BC}}}$).

\subsection{Analytical Performance Evaluation\label{sub:CTUpp_Numerical_Evaluation_uncoded}}

Since all constellations points lie on a regular QAM grid, it is straightforward
to evaluate the exact Symbol Error Rate (SER) for all channels analytically.
The symbol error probability $P_{e}^{\mathrm{SER}}$ can be approximated
by its upper-bound\footnote{The evaluated $P_{e,\mathrm{UB}}^{SER}$ is an upper-bound of $P_{e}^{\mathrm{SER}}$,
since an error in MA/BC phase does not necessarily induce an error
in the overall communication chain of the uncoded system. This is
especially true if the error occurs in the superposed bits $\mathbf{d}_{B}^{s}$
used for interference cancellation processing at $D_{A}$.} $P_{e,\mathrm{UB}}^{\mathrm{SER}}=1-((1-P_{e}^{{\rm MAC}})(1-P_{e}^{{\rm HSI}})(1-P_{e}^{\mathrm{BC}}))$,
where $P_{e}^{{\rm MAC}}$, $P_{e}^{{\rm HSI}}$ and $P_{e}^{{\rm BC}}$
are the probabilities of symbol error in the MAC, HSI and BC channels
(respectively). Since the system is memoryless, the overall FER is
given by $P_{e}^{\mathrm{FER}}=1-(1-P_{e}^{\mathrm{SER}})^{M}$, which
can be approximated by $P_{e,\mathrm{UB}}^{\mathrm{FER}}=1-(1-P_{e,\mathrm{UB}}^{\mathrm{SER}})^{M}$.
Nearest neighbor pairwise error approximation can be used for efficient
error rate evaluation. The lower-bound of the throughput can be then
evaluated analytically as:
\begin{equation}
T_{\mathrm{LB}}=(N_{b}+N_{s})\cdot(1-P_{e,\mathrm{UB}}^{\mathrm{FER}}).\label{eq:CTUpp_T-LB}
\end{equation}

\subsection{Hardware Implementation\label{sub:CTUpp_Hardware_Verification}}

In addition to the analytical evaluation of throughput, we validate
the results in a real-world setup. The hardware performance is evaluated
using Ettus Research Universal Software Radio Peripherals (USRPs)
which are computer-hosted Software Defined Radios (SDRs). The USRPs
connect to a host computer via a Gigabit Ethernet link, which the
host-based software uses to receive and transmit the baseband IQ stream.
The host controls the USRP using USRP Hardware Driver (UHD) commands,
including setting parameters such as amplifier gain. The USRP then
performs the necessary baseband processing then up/down-conversion
and transmission/reception. The Ettus Research N210 USRP is used,
which consists of a motherboard and a Radio Frequency (RF) daughterboard;
more details can be found in \cite{Ettus_flyer}. In these experiments
the XCVR2450 daughterboards are used, these are dual-band transceivers
with 100 mW output at 2.4 - 2.5 GHz and 50 mW output at 4.9 - 5.85
GHz. In this paper GNURadio \cite{GNURadio}, which is an open-source
tool-kit, is used as the host-processing software.

\subsubsection{OFDM Parameters}

An OFDM solution is employed with $N_{FFT}=64$ subcarriers. There
are 48 data subcarriers, with a DC carrier, 11 guard carriers and
4 pilot carriers at -21, -7, 7 and 21. A CP of $\frac{1}{4}$, i.e.
16 samples, is employed and a center frequency of $f_c=2.4$GHz is
used. The USRP N210 is limited (by the Gigabit Ethernet link) to support
an RF bandwidth up to 25 MHz with 14-bit resolution, though a 1 MHz
bandwidth, i.e. 1 MS/s sampling rate, is used here. Each packet contains
16 OFDM symbols of payload with 48 data carriers per symbol and constellation
parameters $N_{b}$,~$N_{s}$ are set to the desired values. The
payload is random data and no channel coding is currently implemented
in the system.

\subsubsection{Node Placement, Synchronization and Channel Estimation\label{sub:CTUpp_frame-1-2}}

>>>>

\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{array}
\usepackage{float}
\usepackage{units}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[dvips]{graphicx}
\usepackage{tikz}
\usetikzlibrary[arrows,calc,decorations.pathmorphing,backgrounds,positioning,fit,petri,shapes,decorations.markings]
\usepackage{pgfplots}
\newcommand{\lyxdot}{.}

\begin{document}
\begin{figure}
\centering{}\includegraphics[width=0.6\columnwidth]{fig/2-SRN-sc_principle_BC-TWT_v4}
\caption{Symmetric WBN model with half-duplex constraint and 2-phase communication.\label{fig:CTUpp_Information_flows}}
\end{figure}

\begin{figure*}
\begin{centering}
\includegraphics[width=1\textwidth]{fig/butterfly-2level_processing_principleTWC-uncoded}
\par\end{centering}
\caption{Relaying scheme for the uncoded WBN
system. DEM stands for a hard decision demodulator, IC is the interference
canceler.\label{fig:CTUpp_Information-flow-uncoded-block-scheme}}
\end{figure*}

\begin{figure*}
\centering{}\includegraphics[width=0.8\textwidth]{fig/d2_1}\caption{Source constellation design example for $N_{b}=2,\,N_{s}=1$. Resulting
constellations are depicted as blue circles ($S_{A}$ output constellation),
red circles ($S_{B}$ output constellation) and squares (received
superimposed constellation at $R$). Hierarchical function is $f\left(\mathbf{d}_{A}^{b},\,\mathbf{d}_{B}^{b}\right)=\mathbf{d}_{A}^{b}\oplus\mathbf{d}_{B}^{b}$.\label{fig:CTUpp_ConstellationDesignExample} }
\end{figure*}

\begin{figure*}
\begin{centering}
\includegraphics[width=1\textwidth]{fig/const_all_2}
\par\end{centering}
